In this work, we analyze the \KS problem and provide descriptions for various algorithms. We primarily focus on the most common form of analysis for the \KS problem (competitive analysis). We provide an overview of various theorems and proofs taken from~\cite{OnlineComp1998}, and additionally go over a fast min-cut max-flow formulation for computing the $\mathrm{WFA}$ movement~\cite{mcfp2011}. We then transition to focusing on the Unifying Potential~\cite{unifyingPotential2021}, overviewing a few of their definitions and proofs. We attempt to extend their methods for multiray spaces to reduced caterpillar graphs. We consider the symetry property they demonstrate for their modified potential, and attempt to extend this to our reduced caterpillar graphs. Finally, we describe various other analysis methods used in the context of this problem, including bijective analysis, the Max-Max ratio, and a modified average case analysis. We provide an open-source software framework for testing and comparing these algorithms in various environments, as well as a framework for generating metric spaces and input sequences. The software package can be found here: \url{https://github.com/StefanCaldararu/KServers}. We finally provide some experimental results derived using this software, and a brief description of these results.

Potential future extensions of this work would primarily include a completion of the extension of the unifying potential to the reduced caterpilar graphs. This may lead to a potential extension to general tree graphs, and potentially to general metric spaces. Additionally, we could extend the experimental analysis to a wider variety of metric spaces. With more time alloted to computation, we could additionally run experiments on longer request sequences, which may offer further valuable insights.